\section{Abstract}
\label{sec:Abstract}
Accurate forecasting and correlation analysis of financial risks are crucial for maintaining market stability and guiding regulatory decision-making. However, traditional econometric and statistical models often fail to capture the nonlinear, non-stationary, and interdependent nature of modern financial systems. This project proposes a unified multimodal Transformer-based framework for the dynamic prediction and correlation analysis of credit risk, market risk, and liquidity risk. The model integrates dynamic time-series data (e.g., daily K-line, returns, volatility, and trading volume) with static structural data (e.g., corporate financial statements, leverage ratios, and macroeconomic indicators) to jointly learn temporal evolution and firm-level fundamentals. A cross-modal attention mechanism is employed to fuse heterogeneous features, while frequency decomposition techniques (such as EMD and CEEMDAN) are used to extract multi-scale components and suppress noise. The resulting hybrid architecture enables long-term dependency modeling and interpretable risk estimation across multiple dimensions. Empirical evaluations on large-scale market datasets will assess predictive accuracy, robustness, and interpretability compared with benchmark models such as LSTM and VAR. This research aims to provide a data-driven, explainable framework for systemic financial risk assessment, offering new insights into the dynamic interrelations among credit, market, and liquidity risks.